---
title: "Coverage Assessment of Direct Nutrition Interventions in Liberia"
author: ""
date: #'`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)

if(!require(remotes)) install.packages("remotes")
if(!require(magrittr)) install.packages("magrittr")
if(!require(leaflet)) install.packages("leaflet")
if(!require(RColorBrewer)) install.packages("RColorBrewer")
if(!require(rgdal)) install.packages("rgdal")
if(!require(rgeos)) install.packages("rgeos")
if(!require(raster)) install.packages("raster")
if(!require(xaringan)) install.packages("xaringan")

if(!require(ggplot2)) install.packages("ggplot2")
if(!require(cowplot)) install.packages("cowplot")

if(!require(liberia)) remotes::install_github("validmeasures/liberia")
if(!require(liberiaData)) remotes::install_github("validmeasures/liberiaData")
if(!require(xaringanthemer)) remotes::instal_github("gadenbuie/xaringanthemer")

mapbox.satellite <- "https://api.mapbox.com/styles/v1/mapbox/satellite-streets-v10/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.street    <- "https://api.mapbox.com/styles/v1/mapbox/streets-v10/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.dark      <- "https://api.mapbox.com/styles/v1/mapbox/dark-v9/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.light     <- "https://api.mapbox.com/styles/v1/mapbox/light-v9/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.moonlight <- "https://api.mapbox.com/styles/v1/ernestguevarra/cj3nban30001z2rpahc10c9ef/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.northstar <- "https://api.mapbox.com/styles/v1/ernestguevarra/cj4ke832y4sng2spe2ds4fs55/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.standard  <- "https://api.mapbox.com/styles/v1/ernestguevarra/cj5di36jn0gxg2rphjn3yetpt/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.decimal   <- "https://api.mapbox.com/styles/v1/ernestguevarra/cj5ms1akt3pbi2smtcewsex9m/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"
mapbox.terminal  <- "https://api.mapbox.com/styles/v1/ernestguevarra/cj6g0tzbd30kc2sph2wyh666m/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1IjoiZXJuZXN0Z3VldmFycmEiLCJhIjoiejRRLXlZdyJ9.sqS1zi0rDH5CIzvcn9SXSg"

monrovia <- subset(liberia::districts, admin2Name == "Greater Monrovia")
gmLng1 <- bbox(monrovia)[1, 1]
gmLat1 <- bbox(monrovia)[2, 1]
gmLng2 <- bbox(monrovia)[1, 2]
gmLat2 <- bbox(monrovia)[2, 2]

gmLng <- coordinates(monrovia)[1]
gmLat <- coordinates(monrovia)[2]

ifaBase <- readOGR(dsn = "data/ifa", layer = "ifaPolyGM")
icfBase <- readOGR(dsn = "data/icf", layer = "icfPolyGM")
mnpBase <- readOGR(dsn = "data/mnp", layer = "mnpPolyGM")
vitBase <- readOGR(dsn = "data/vit", layer = "vitPolyGM")
screenBase <- readOGR(dsn = "data/screen", layer = "screenPolyGM")
cmamBase <- readOGR(dsn = "data/cmam", layer = "coveragePolyGM")
nutBase <- readOGR(dsn = "data/nut", layer = "nutPolyGM")

covHex <- gmHexGrid
covHex@data <- data.frame(covHex@data, ifaInt, iycfInt, mnpInt, vitInt, screenInt, cmamInt, anthroInt)

map.palette <- colorRampPalette(colors = brewer.pal(n = 7, name = "RdYlGn"), 
                                space = "Lab")

themeSettings <- theme_bw() + 
  theme(panel.border = element_rect(colour = "#993300",
                                    size = 0.5),
        panel.grid.major = element_line(linetype = 1, 
                                        size = 0.2, 
                                        colour = "gray90"),
        panel.grid.minor = element_line(linetype = 0),
        strip.background = element_rect(colour = "#993300",
                                        fill = "#993300"),
        strip.text = element_text(colour = "white", size = 16),
        legend.key = element_rect(linetype = 0),
        axis.text.y.left = element_text(size = 18),
        axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 18),
        axis.ticks = element_line(colour = "#993300", size = 1))
```

```{r xaringan-themer, include = FALSE}
xaringanthemer::mono_light(
  base_color = "#85010C", #CF070C",
  #title_slide_background_image = "https://www.validnutrition.org/wp-content/uploads/2017/07/Valid-Nutrition-CMAM.jpg",
  #title_slide_background_size = "cover",
  header_font_google = google_font("Lato"),
  text_font_google = google_font("EB Garamond"),
  text_color = "#2D2D2D",
  text_bold_color = "#247BA0",
  text_font_size = "1.5em",
  code_font_google = google_font("Fira Mono"),
  text_slide_number_font_size = "0.75em"
)
```

class: inverse, center, middle

## Valid International Ltd

www.validinternational.org

`r Sys.Date()`

---
# Outline

* Iron-folic acid supplementation coverage

* Infant and young child feeding counselling coverage

* Micronutrient powder supplementation coverage

* Vitamin A supplementation coverage

* Nutrition screening coverage

* CMAM coverage

---
background-color: #FFFFFF

# Iron-folic acid supplementation coverage

```{r ifa, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
xlabs <- c("At least one\nANC visit",
           "Know/heard\nof IFA",
           "Received/\npurchased IFA",
           "Consumed\nIFA",
           "Consumed\nIFA\nat least\n90 days")

ifaEst <- read.csv("data/ifaEst.csv")
ifaEst <- ifaEst[ifaEst$county == "Monrovia", ]

baseline <- ggplot(data = ifaEst[ifaEst$type == "est" & 
                                   ifaEst$indicator %in% c("ifa1", 
                                                           "ifa2", 
                                                           "ifa3", 
                                                           "ifa4", 
                                                           "ifa5"), ],
                   aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = 0:1 * 100, 
                     breaks = seq(from = 0, to = 100, by = 10)) + 
  scale_x_discrete(labels = xlabs) + 
  themeSettings

endline <- ggplot(data = ifaBoot[ifaBoot$varLabel %in% c("ifa1", 
                                                         "ifa2", 
                                                         "ifa3",
                                                         "ifa4", 
                                                         "ifa6"), ], 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10),
                     limits = c(0, 100)) +
  scale_x_discrete(labels = xlabs) +
  labs(x = "", y = "%") +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# Spatial distribution of IFA coverage

```{r ifaMap, echo = FALSE, eval = TRUE, fig.width = 25, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(2, 5))

varLab <- c("ifa1", "ifa2", "ifa3", "ifa4", "ifa5")
varName <- c("At least one ANC visit",
             "Know/heard of IFA",
             "Received/ purchased IFA",
             "Consumed IFA",
             "Consumed IFA at least 90 days")

for(i in 1:length(varLab)) {
  plot(ifaBase, lty = 0, col = map.palette(n = 101)[(ifaBase[[varLab[i]]] * 100) + 1])
  title(main = paste("Baseline: ", varName[i], sep = ""), cex = 15, line = -1)
}

varLab <- c("ifa1", "ifa2", "ifa3", "ifa4", "ifa6")

for(i in 1:length(varLab)) {
  plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[[varLab[i]]] * 100) + 1])
  title(main = paste("Endline: ", varName[i], sep = ""), cex = 15, line = -1)
}
```

---
background-color: #FFFFFF

# IYCF counselling

```{r icf, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
xlabs <- c("Know about\nIYCF counselling", 
           "Attended IYCF\ncounselling")

icfEst <- read.csv("data/icfEst.csv")
icfEst <- icfEst[icfEst$county == "Monrovia", ]

baseline <- ggplot(data = icfEst[icfEst$indicator %in% c("icf1", "icf2"), ], 
                   mapping = aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = 0:1 * 100, 
                     breaks = seq(from = 0, to = 100, by = 10)) + 
  scale_x_discrete(labels = xlabs) + 
  themeSettings

endline <- ggplot(data = iycfBoot[iycfBoot$varLabel %in% c("icf1", 
                                                           "icf2"), ], 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10),
                     limits = c(0, 100)) +
  scale_x_discrete(labels = xlabs) +
  labs(x = "", y = "%") +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# Spatial distrubtion of IYCF counselling coverage

```{r icfMap1, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(1, 2))

plot(icfBase, lty = 0, col = map.palette(n = 101)[(icfBase[["icf1"]] * 100) + 1])
title(main = "Baseline: Know about IYCF counselling", cex = 1, line = -1)

plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[["icf1"]] * 100) + 1])
title(main = "Endline: Know about IYCF counselling", cex = 1, line = -1)
```

---
background-color: #FFFFFF

# Spatial distrubtion of IYCF counselling coverage

```{r icfMap2, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(1, 2))

plot(icfBase, lty = 0, col = map.palette(n = 101)[(icfBase[["icf2"]] * 100) + 1])
title(main = "Baseline: Attended IYCF counselling", cex = 1, line = -1)

plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[["icf2"]] * 100) + 1])
title(main = "Endline: Attended IYCF counselling", cex = 1, line = -1)
```

---
background-color: #FFFFFF

# Micronutrient powder supplementation coverage

```{r mnp, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
xlabs <- c("Know/heard\nabout\nMNP",
           "Received/\npurchased\nMNP",
           "Consumed\nMNP")

mnpEst <- read.csv("data/mnpEst.csv")
mnpEst <- mnpEst[mnpEst$county == "Monrovia", ]

baseline <- ggplot(data = mnpEst[mnpEst$indicator %in% c("mnp1", "mnp2", "mnp3"), ], 
                   mapping = aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = c(0, 100), 
                     breaks = seq(from = 0, to = 100, by = 10)) + 
  scale_x_discrete(labels = xlabs) + 
  themeSettings

endline <- ggplot(data = mnpBoot[mnpBoot$varLabel %in% c("mnp1", "mnp2", "mnp3"), ], 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10),
                     limits = c(0, 100)) +
  scale_x_discrete(labels = xlabs) +
  labs(x = "", y = "%") +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# Spatial distribution of MNP supplementation coverage

```{r mnpMap, echo = FALSE, eval = TRUE, fig.width = 9, fig.height = 6, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(2, 3))

varLab <- c("mnp1", "mnp2", "mnp3")
varName <- c("Know/heard about MNP",
              "Received/purchased MNP",
              "Consumed MNP")

for(i in 1:length(varLab)) {
  plot(mnpBase, lty = 0, col = map.palette(n = 101)[(mnpBase[[varLab[i]]] * 100) + 1])
  title(main = varName[i], cex = 1, line = -1)
}

for(i in varLab) {
  plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[[i]] * 100) + 1])
}
```

---
background-color: #FFFFFF

# Vitamin A supplementation coverage

```{r vit, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
xlabs <- c("Received\nvitamin A\nin past 6 months")

vitEst <- read.csv("data/vitEst.csv")
vitEst <- vitEst[vitEst$county == "Monrovia", ]

baseline <- ggplot(data = vitEst[vitEst$indicator %in% "vit1", ], 
                   mapping = aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.5, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = 0:1 * 100, 
                     breaks = seq(from = 0, to = 100, by = 10)) + 
  scale_x_discrete(labels = xlabs) + 
  themeSettings

endline <- ggplot(data = vitBoot[vitBoot$varLabel %in% "vit1", ], 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.5, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10),
                     limits = c(0, 100)) +
  scale_x_discrete(labels = xlabs) +
  labs(x = "", y = "%") +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# Spatial distribution of vitamin A supplementation coverage

```{r vitMap, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(1, 2))

plot(vitBase, lty = 0, col = map.palette(n = 101)[(vitBase[["vit1"]] * 100) + 1])
title(main = "Baseline: Received vitamin A in past 6 months", cex = 1, line = -1)

plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[["vit1"]] * 100) + 1])
title(main = "Endline: Received vitamin A in past 6 months", cex = 1, line = -1)
```

---
background-color: #FFFFFF

# Nutrition screening

```{r screen, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
xlabs <- c("MUAC\nscreening", 
           "Oedema\nscreening")

screenEst <- read.csv("data/screenEst.csv")
screenEst <- screenEst[screenEst$county == "Monrovia", ]

screenEst$indicator <- factor(screenEst$indicator, levels = c("muacScreen", "oedemaScreen", "bothScreen"))

baseline <- ggplot(data = screenEst[screenEst$indicator %in% c("muacScreen", "oedemaScreen"), ], 
       aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.5, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = c(0, 1) * 100, 
                     breaks = seq(from = 0, to = 100, by = 20)) + 
  scale_x_discrete(labels = xlabs) + 
  themeSettings

endline <- ggplot(data = screenBoot[screenBoot$varLabel %in% c("height.screen", "weight.screen", 
                                                              "muac.screen", "oedema.screen"), ], 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.5, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 20),
                     limits = c(0, 100)) +
  labs(x = "", y = "%") +
  scale_x_discrete(labels = c("Height\nscreening", "Weight\nscreening", 
                              "MUAC\nscreening", "Oedema\nscreening")) +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# CMAM coverage

```{r cmam, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10}
coverageEst <- read.csv("data/coverageEst.csv")
coverageEst <- coverageEst[coverageEst$county == "Monrovia", ]

coverageEst$indicator <- factor(coverageEst$indicator, levels = c("point", "treatment"))

baseline <- ggplot(data = coverageEst[coverageEst$indicator %in% c("point", "treatment"), ], 
                   mapping = aes(x = indicator, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  labs(x = "", y = "%") +
  scale_y_continuous(limits = c(0, 1) * 100, 
                     breaks = seq(from = 0, to = 100, by = 10)) + 
  scale_x_discrete(labels = c("Case-finding effectiveness", 
                              "Treatment coverage")) + 
  themeSettings

endline <- ggplot(data = cmamEst, 
                  mapping = aes(x = varLabel, y = estimate * 100)) +
  geom_col(color = "#993300", fill = "#993300", width = 0.7, alpha = 0.7) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 20),
                     limits = c(0, 100)) +
  labs(x = "", y = "%") +
  scale_x_discrete(labels = c("Case-finding effectiveness", "Treatment coverage")) +
  themeSettings

plot_grid(baseline, endline, labels = c("Baseline", "Endline"), 
          label_size = 28, label_colour = "#85010C")
```

---
background-color: #FFFFFF

# Spatial distribution of CMAM coverage

```{r cmamMap1, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(1, 2))

plot(cmamBase, lty = 0, col = map.palette(n = 101)[(cmamBase[["case"]] * 100) + 1])
title(main = "Baseline: Case-finding effectiveness", cex = 1, line = -1)

plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[["cf"]] * 100) + 1])
title(main = "Endline: Case-finding effectiveness", cex = 1, line = -1)
```

---
background-color: #FFFFFF

# Spatial distribution of CMAM coverage

```{r cmamMap2, echo = FALSE, eval = TRUE, fig.width = 20, fig.height = 10, fig.align = "center"}
par(mar = c(0, 0, 0 ,0), mfrow = c(1, 2))

plot(cmamBase, lty = 0, col = map.palette(n = 101)[(cmamBase[["treatment"]] * 100) + 1])
title(main = "Baseline: Case-finding effectiveness", cex = 1, line = -1)

plot(covHex, lty = 0, col = map.palette(n = 101)[(covHex[["tc"]] * 100) + 1])
title(main = "Endline: Case-finding effectiveness", cex = 1, line = -1)
```

